SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-07-01 scipy-1.0/paper.tex
Language choices subsection now distinguishes Cython & Python
* we now use a custom branch of linguist to parse Cython
and Python source components separately
* the SciPy library language composition Figure is now
generated using TikZ to facilitate modification

Co-authored-by: Ilhan Polat <ilhanpolat@gmail.com>

% Packages
\usepackage[super]{nth}
\usepackage{rotating}
\usepackage{makecell}
\usepackage{pifont}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{float}

@@

\subsection*{Language choices}
Python / Cython, Fortran, C and C++ are the programming languages
used to implement scientific algorithms in the SciPy library. An analysis
of our code base using the \texttt{linguist} library provides a detailed
breakdown as \% composition by programming language in SciPy
(Figure~\ref{fig:linguist}).

    \begin{figure}[H]
        \centering
        \includegraphics[width=\textwidth]{static/linguist}
        \caption{The breakdown of programming languages used in the
	         SciPy library determined using the linguist library.
		 Small ($<0.5 \%$) amounts of TeX, Matlab, Shell,
		 and Makefile are excluded for clarity and mostly
		 provide supporting roles in tests, building, and
		 documentation.}
        \label{fig:linguist}
    \end{figure}

>>>>

% Packages
\usepackage[super]{nth}
\usepackage{rotating}
\usepackage{makecell}
\usepackage{pifont}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{float}
\usepackage{pgfplots}

\pgfplotsset{compat=newest}

@@

\subsection*{Language choices}
Python, Cython, Fortran, C and C++ are the programming languages
used to implement scientific algorithms in the SciPy library. An analysis
of our code base using the \texttt{linguist} library provides a detailed
breakdown as \% composition by programming language in SciPy
(Figure~\ref{fig:linguist}).

    \begin{figure}[H]
        \centering

        \begin{tikzpicture}[font=\sffamily]
        \begin{axis}[height=6cm, width=10cm,
        ybar, ymax=60, ymin=0,bar width=1cm,
        ylabel={\% of Scipy code base},
        ytick={0,20,...,60},
        axis lines*=left,
        axis y line shift=0pt,
        enlarge x limits=0.15,
        symbolic x coords={py,f,c,cy,cpp},
        xticklabels={Python,FORTRAN,C,Cython,C++},
        ticklabel style={align=center,font=\sffamily\small,
        /pgf/number format/assume math mode=true},
        xtick=data,
        nodes near coords,
        nodes near coords style={/pgf/number format/assume math mode=true}
        ]
        \addplot coordinates {(py,49.5) (f,25.6) (c,19.5) (cy, 3.0) (cpp,2.3)};
        \end{axis}
        \end{tikzpicture}
        \caption{The breakdown of programming languages used in the
	         SciPy library determined using the linguist library.
		 Small ($<0.5 \%$) amounts of TeX, Matlab, Shell,
		 and Makefile are excluded for clarity and mostly
		 provide supporting roles in tests, building, and
		 documentation.}
        \label{fig:linguist}
    \end{figure}
